



```{r}
peas <- read.table(text="
parent,offspring
0.21,0.1726
0.20,0.1707
0.19,0.1637
0.18,0.1640
0.17,0.1613
0.16,0.1617
0.15,0.1598", header=TRUE, sep=",")

pea <- read.table(text="parent,offspring
0.21,0.1726
0.20,0.1707
0.19,0.1637", header=TRUE, sep=",")

out.mod <- lm(offspring~parent, data=pea)
summary(out.mod)



cor(peas$parent, peas$offspring)
plot(offspring~parent, data=peas)
```
In-Class Work 1/31/2018

Objective: Scientific Evidence
Model: yi = B0 + B1xi + Ei, Ei~N(0,O^2)
Analysis:
     Estimate B0, B1, O^2 and measure of uncertainty (Standard Error of B0 and B1)
     Interpret what the scientific effect is
     Inference/Test
     Graphic
     
```{r}
#model: offspring = beta0 + beta1 parent+ epsilon, epsilon~N(0,sigma2)

#Fit Model/Estimate the Model Parameters
out.peas<-lm(offspring~parent, data=peas)

#See parameter estimates and standard errors
summary(out.peas)        #Beta0hat is intercept and beta1 is parent
beta1hat <- 0.21         #estimated slope of inheritance effect is 0.21
beta0hat <- 0.127029
sigma2 <- 0.002043^2

#There is a statistically significant inheritance effect (p-value=0.002852)
```


Test H0: B1=0
t-test
ANOVA

Both are the same, but sometimes one is easier to do than the other. we will learn more about it later
Create a 95% CI on B1
```{r}
#pvalue for h0: B1 is above
#95% CI on B1 is (0.1107, 0.3093)
confint(out.peas)
```
#Conclusion
There is a statistically significant inheritance effect in sweet pea diameters (pavlue=0.002852).
For a one unit increase in parent sweet pea diameter, we expect an increase of 0.21 (95% CI: 0.1107, 0.3093) in offspring sweet pea diameter.

```{r}
#Create a graphic showing estimated line and uncertainty
library(ggplot2)
qplot(parent, offspring, data=peas,
      geom="smooth", formula=y~x, method="lm", se=TRUE,
      xlab="Diameter of Parent Pea",
      ylab="Diameter of Offspring Pea")
```
95% CI of mean of all offspring diameter with Parent = 0.2
```{r}
predict(out.peas, newdata=data.frame(parent=0.2), interval="confidence")
```

If we are interested in prediciton...
95% Prediction interval(PI) of a new offspring diameter with parent = 0.18
```{r}
predict(out.peas, newdata=data.frame(parent=0.18), interval="prediction")
```

Graphic to demonstrate prediction performance
```{r}
plot.df <- cbind(peas, predict(out.peas, interval="prediction"))
ggplot(plot.df, aes(parent, offspring)) + xlab("Diameter of Parent Pea") + geom_point() + 
  geom_line(aes(y=fit), color="royalblue") + geom_line(aes(y=lwr), color="red", linetype="dashed") +
  geom_line(aes(y=upr), color="red", linetype="dashed")
```































