# Montgomery County, Maryland Traffic Stops Data

Read in Data
```{r}
stops.full<-read.csv("http://data.montgomerycountymd.gov/api/views/4mse-ku6q/rows.csv?accessType=DOWNLOAD",
                     header=TRUE,as.is=TRUE)

# subset to last year
last.year<-2017
stops.full$AutoYear<-as.numeric(stops.full$Year)
stops.full$Year<-as.numeric(substr(stops.full$Date.Of.Stop,7,10))
stops.last<-subset(stops.full,Year==last.year)

rm(stops.full)

# Create Month and Hour variables
stops.last$Month<-as.numeric(substr(stops.last$Date.Of.Stop,1,2))
stops.last$Hour<-as.numeric(substr(stops.last$Time.Of.Stop,1,2))

# clean up dataset
stops.last$AutoState<-stops.last$State
stops.last$Out.of.State<-(stops.last$AutoState!="MD")

stops.last$Color<-as.character(stops.last$Color)
stops.last$Color[stops.last$Color %in% c("CAMOUFLAGE","CHROME","COPPER","CREAM","MULTICOLOR","N/A","PINK")]<-"OTHER"
stops.last$Color<-factor(stops.last$Color)

# other filters
stops.last<-subset(stops.last,Color != "N/A")
stops.last<-subset(stops.last,Color != "")
stops.last<-subset(stops.last,Gender != "U")
stops.last<-subset(stops.last,HAZMAT == "No")
stops.last<-subset(stops.last,AutoYear > 1990 & AutoYear < last.year+2)

# convert character variables to factors
stops.last$SubAgency<-factor(stops.last$SubAgency)
stops.last$Accident<-factor(stops.last$Accident)
stops.last$Belts<-factor(stops.last$Belts)
stops.last$Personal.Injury<-factor(stops.last$Personal.Injury)
stops.last$Property.Damage<-factor(stops.last$Property.Damage)
stops.last$Commercial.License<-factor(stops.last$Commercial.License)
stops.last$Commercial.Vehicle<-factor(stops.last$Commercial.Vehicle)
stops.last$Alcohol<-factor(stops.last$Alcohol)
stops.last$Work.Zone<-factor(stops.last$Work.Zone)
stops.last$Contributed.To.Accident<-factor(stops.last$Contributed.To.Accident)
stops.last$Race<-factor(stops.last$Race)
stops.last$Gender<-factor(stops.last$Gender)
stops.last$Out.of.State<-factor(stops.last$Out.of.State)


# Create dataset for Speeding
#  example: EXCEEDING MAXIMUM SPEED: 49 MPH IN A POSTED 40 MPH ZONE
speed.last1<-subset(stops.last,substr(Description,1,23)=="EXCEEDING MAXIMUM SPEED")
# difference between cited speed and posted speed limit
speed.last1$speed<-as.numeric(substr(speed.last1$Description,26,27))-as.numeric(substr(speed.last1$Description,45,46))
speed.last1<-subset(speed.last1,!is.na(speed))
#  example: EXCEEDING POSTED MAXIMUM SPEED LIMIT: 39 MPH IN A POSTED 30 MPH ZONE
speed.last2<-subset(stops.last,substr(Description,1,30)=="EXCEEDING POSTED MAXIMUM SPEED")
# difference between cited speed and posted speed limit
speed.last2$speed<-as.numeric(substr(speed.last2$Description,39,40))-as.numeric(substr(speed.last2$Description,58,59))
speed.last2<-subset(speed.last2,!is.na(speed))
# combine and subset to columns of interest
speed.last<-rbind(speed.last1,speed.last2)
speed.last<-speed.last[,c(4,9:12,14,16:18,24,28:30,36:38,40,41)]


# Create dataset for Ticket/Warning
ticket.last<-subset(stops.last,Violation.Type %in% c("Citation","Warning") )
ticket.last$Ticket<-factor(ticket.last$Violation.Type=="Citation")
# subset to columns of interest
ticket.last<-ticket.last[,c(4,9:12,14,17,18,24,28:30,36:38,40,41)]


# make a prediction at a new observation
#  note: grab an observation in the dataset that is very similar to my situation and change it
new.obs<-speed.last[25,]
new.obs$AutoYear<-2017
new.obs$Month<-8
new.obs$Hour<-18


#Response Variable: Speed
#Explanatory Variables
head(speed.last)
summary(speed.last)
```

EDA
```{r}
summary(speed.last$speed)
```

Create Train & Test
```{r}
set.seed(12)
train.rows <- sample(9773, 8000)
speed.train <- speed.last[train.rows,]
speed.test <- speed.last[-train.rows,]

summary(speed.train$speed)
summary(speed.test$speed)
```

Create RF
```{r}
#install.packages("randomForest")
library(randomForest)
out.speed <- randomForest(x=speed.train[,-18], y=speed.train$speed,
                          xtest=speed.train[,-18], ytest=speed.test$speed, 
                          replace=TRUE, keep.forest=TRUE, ntree=50, mtry=5,
                          nodesize=30)
```

Compare train prediction error and test prediction error
SRS without replacement of n.train=8000
```{r}
#Predict a new observation
new.obs
predict(out.speed, newdata=new.obs)


#Compare train and test RMSE
out.speed

#train rmse
sqrt(49.08494)

#test rmse
sqrt(50.25)


#model interpretability (how often were explanatory variables used)
importance(out.speed)
varImpPlot(out.speed)
```

Explanatory Variables - if I were to guess, I would say that the distrit the agency that pulled them over is the biggest factor as to if they got a ticket or not
```{r}
head(ticket.last[,-17])


#EDA
table(ticket.last$Ticket)
prop.table(table(ticket.last$Ticket))
```

Create dataset with half goods (warnings) and half bads(tickets)
```{r}
all.bad <- subset(ticket.last, Ticket=="TRUE")
n.bad<-dim(all.bad)[1]

#SRS without replacement of goods
all.good<-subset(ticket.last,Ticket=="FALSE")
n.good<-dim(all.good)[1]
set.seed(12)
rows.good<-sample(n.good,n.bad)
sample.good<-all.good[rows.good,]

#Combine
ticket.model<-rbind(all.bad,sample.good)
```

Make train & test
```{r}
summary(ticket.model)
set.seed(7980)
gbtrainrows <- sample(61598, 49000)
gbtrain <- ticket.model[gbtrainrows,]
gbtest <- ticket.model[-gbtrainrows,]

summary(gbtrain)
summary(gbtest)

randomForest(x=gbtrain[,-17], y=)

summary(ticket.last)
```


