1. ARIMA time series models make assumptions about the possible trend, stationarity, and distribution of the data. For each of the following national parks:

 - Download the Annual Park Recreation Visitation data and write documented reproducible code to create an    appropriate R dataframe.
 - Plot the time series for annual visitors (in millions)
 - Identify a significant feature of the time series that violates the ARIMA model assumptions. Research     why the data exhibits this unusual feature
 
  (a) Washington Monument
  (b) Jefferson Memorial
  (c) Wright Bros Memorial
  (d) Acadia
  
```{r}
#Washington Monument Analysis

wash <- read.csv("Washington Monument Visitors.csv", header=TRUE, sep=",")  #Reads in data to df
wash$RecreationVisitors <- as.numeric(gsub(',','',wash$RecreationVisitors)) #Takes out commas
wash$RecreationVisitors <- wash$RecreationVisitors/10^6                     #Changes visitors to millions
plot(RecreationVisitors~ï..Year, data=wash, type="b", ylab="Washington Monument NP Annual Visitors (in millions)")

#Jefferson Memorial Analysis

jeff <- read.csv("Jefferson Memorial Visitors.csv", header=TRUE, sep=",")  
jeff$RecreationVisitors <- as.numeric(gsub(',','',jeff$RecreationVisitors)) 
jeff$RecreationVisitors <- jeff$RecreationVisitors/10^6                     
plot(RecreationVisitors~ï..Year, data=jeff, type="b", ylab="Jefferson Memorial NP Annual Visitors (in millions)")

#Wright Bros Analysis

bros <- read.csv("Wright Bros Memorial.csv", header=TRUE, sep=",")  
bros$RecreationVisitors <- as.numeric(gsub(',','',bros$RecreationVisitors)) 
bros$RecreationVisitors <- bros$RecreationVisitors/10^6                     
plot(RecreationVisitors~ï..Year, data=bros, type="b", ylab="Wright Bros Memorial NP Annual Visitors (in millions)")

#Acadia Analysis

aca <- read.csv("Acadia.csv", header=TRUE, sep=",")  
aca$RecreationVisitors <- as.numeric(gsub(',','',aca$RecreationVisitors))
aca$RecreationVisitors <- aca$RecreationVisitors/10^6                 

plot(RecreationVisitors~ï..Year, data=aca, type="b", ylab="Acadia NP Annual Visitors (in millions)")

```
  
  
C. Download the Annual Park Recreation Visitation data and write documented reproducible code to create an appropriate R dataframe
```{r}
linc <- read.csv("Lincoln.csv", header=TRUE, sep=",")  #Reads in data to df
linc$RecreationVisitors <- as.numeric(gsub(',','',linc$RecreationVisitors)) #Takes out commas
linc$RecreationVisitors <- linc$RecreationVisitors/10^6                     #Changes visitors to millions
```
  
D. Plot the time series for visitation (in millions) and comment on the validity of the ARIMA model assumptions.
```{r}
plot(RecreationVisitors~ï..Year, data=linc, type="b", ylab="Lincoln Memorial NP Annual Visitors (in millions)")
#Insert comments on analysis
```

E. If you feel filtering to the 'recent past' or a transformation is necessary, explain what you observed and demonstrate why it is better after filtering and/or transforming
```{r}
linc2000 <- subset(linc, ï..Year > 1999)
plot(RecreationVisitors~ï..Year, data=linc2000)
# It doesn't really make sense to transform our data because our model isn't really showing a mulitpolicative curve. What I decided to do was filter to the years 2000 until now because before the year 2000 are such volatile numbers due to different events happening in DC during the time. For example, there's a spike in the 60's due to Civil Right's movements, but there was an uncharacteristic dip where for most of the 90's there were few visitors. I couldn't find a whole lot of information on it, but I learned that the monument was closed for a period of time in the 90's for renovation, and they closed off parts of the monument to public access. I felt that it would affect my prediction negatively, so I filtered from the year 2000 on.
```

F. Fit an ARIMA(1,1,1) model and report the parameter estimates and standard errors
```{r}
library(astsa)
linc2000.out <-sarima(linc2000$RecreationVisitors, 1, 1, 1)
summary(linc2000.out)

#compute predicitons for the next 5 years
linc2000.future <- sarima.for(linc2000$RecreationVisitors, n.ahead=5,1,1,1)
linc2000.future

#computer 95% prediction intervals
linc2000.ci <- linc2000.future$pred + c(-1,1)*qnorm(0.975) * linc2000.future$se


```

